Dynamic Stochastic Approximation Monte Carlo

### 2018-07-25 papers/histogram/sad.tex
added some more recent text on TMMC section

\subsection{TMMC Algorithm}
The Transition Matrix Monte-Carlo (TMMC) method as introduced by
Fitzgerald et al. consists of three primary steps.  The first two steps
are common to the Metropolis algorithm while the third makes use of the
actual transition probabilities~\cite{fitzgerald2000monte}.

>>>>

\subsection{TMMC Algorithm}
{\color{red}
The flat-histogram Wang  and  Landau method utilizes a so-called
``visited states'' approach to calculate  thermodynamic
properties~\cite{errington2003direct}. The algorithm is fundamentally
based on the number of times a given state is visited while the
system is being sampled. The Transition Matrix Monte Carlo (TMMC) method operates
differently than the visited states approach~\cite{fitzgerald2000monte}. The method
uses attempted transitions between states to obtain an estimate of transition probabilities.

Say something about detailed balance here?...

For problems that sample states where the relative probabilities
vary by many orders of magnitude, all of the states will
not be sampled efficiently within reasonable simulation
time without introducing a bias in the sampling distribution.

While the current algorithm is highly efficient, a weighting function $\eta_t$
is introduced to ensure that the system samples all states
evenly~\cite{mahynski2017multivariable, blanco2016effect}.
As for the Flat-histogram approach, the weighting function is
set inversely proportional to the current macrostate probability.
\begin{align}
  \eta(I) = - \ln(D(I))
\end{align}
The probability is defined in terms of this biasing function:
\begin{align}
  p(I\rightarrow J) = \min\bigg[1,\frac{\eta(J)}
  {\eta(I)} e^{\beta (E(I)-E(J))}\bigg]
\end{align}
The TMMC algorithm consists of recording the data in a collection matrix
(the unormalized transition histogram matrix).
\begin{align}
  C(I \rightarrow J) = C(I \rightarrow J) + p(I \rightarrow J)\\
  C(I \rightarrow I) = C(I \rightarrow I) +(1 - p(I \rightarrow J))
\end{align}
If the energy state has not been changed, then $C$ is still incremented by
unity. Fitzgerald et al.~\cite{fitzgerald2000monte} showed that defining
the third step this way results in a uniform improvement over using
histogram estimators to determine the particle number probability
distribution (PNPD). The algorithm is highly efficient due to the ability
to bias the simulation while keeping the criteria used to update the
collection matrix $C(I\rightarrow J)$.
}

The Transition Matrix Monte-Carlo (TMMC) method as outlined by
Fitzgerald et al. consists of three primary steps.  The first two steps
are common to the Metropolis algorithm while the third makes use of the
actual transition probabilities~\cite{fitzgerald2000monte}.
